%!TEX encoding = UTF-8 Unicode
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.4in,right=0.75in,bottom=0.4in]{geometry} % Document margins
\usepackage{CJK}
\usepackage{hyperref}

\begin{CJK}{UTF8}{bsmi}
\name{Tony Lee (Hao-Wei Lee 李豪韋)} % Your name
\address{242 Xinzhuang Dist. New Taipei City, Taiwan(R.O.C.)} % Your address
\address{0922-118-303 \\ tony123930@yahoo.com.tw} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{National Tsing Hua University, Taiwan}{September 2014 - Present}{M.S. in Electrical Engineering}{}
\item Lab: Acoustics and Hearing Group
\item Honor:
	\begin{cvItemize}{$-$}
		\item Scholarship of Electrical Engineering Dept. \hfill September 2014
	\end{cvItemize}
\end{rSubsection}

\begin{rSubsection}{National Tsing Hua University, Taiwan}{September 2010 - June 2014}{B.S. in Electrical Engineering}{}
\item Academics: 3.69/4.3 GPA
\item Projects:
	\begin{cvItemize}{$-$}
		\item Acoustic Reality Transport
		\item Applications Development \href{https://github.com/HW-Lee}{(see more detailed on github://HW-Lee)}
	\end{cvItemize}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{AppUniverz}{July 2014 - October 2014}{Android/iOS Developer}{Taipei City, Taiwan}
\item SGPOC: Main Designer, Maintenance Programmer
	\begin{cvItemize}{$-$}
		\item Developed the app in android/iOS for chemical detection,e.g. pregnant detection and food security, in a month. 
	\end{cvItemize}
\item Boiton: Maintenance Programmer, User Interface Implementer
	\begin{cvItemize}{$-$}
		\item Assisted in accomplishing the app for the industry of insurance and eliminating bugs in it.
	\end{cvItemize}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Gemtek}{July 2013 - September 2013}{Android Developer}{New Taipei City, Taiwan}
\item UtubeBox: UI Implementing, API Programming, Quality Testing
	\begin{cvItemize}{$-$}
		\item Launched the app from beginning to the second phase release.
		\item Built an API retrieving photos from Picasa.
		\item Designed 2 high-customizability widgets for use of android UI in a week.
	\end{cvItemize}
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	LEADERSHIP SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Leadership}

\begin{rSubsection}{Implementation of Technology Commercialization}{2013 September - 2014 June}
{CTO of GoodLife Team, National Tsing Hua University}{Hsinchu, Taiwan}
\item Technical Support \& Implementation
	\begin{cvItemize}{$-$}
		\item Developed an android app named 'VoiceBook' only in a week.
	\end{cvItemize}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Glee Club of National Tsing Hua University}{2011 January - 2012 January}
{Tenor Leader}{Hsinchu, Taiwan}
\item Simple Teaching of Music Theory (簡易樂理教學)
	\begin{cvItemize}{$-$}
		\item Have taught over 20 people to understand the basic music theory.
	\end{cvItemize}
\item Practice Leading (帶練)
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
Programming Skills & C, C++, Objective-C, Java, JavaScript, HTML \\
Protocols \& APIs & JSON, REST, XML \\
Tools & MATLAB, Octave, RStudio, Eclipse for Java/Android, Xcode, \LaTeX
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{CJK}
\end{document}