%!TEX encoding = UTF-8 Unicode
\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{CJK}

\begin{CJK}{UTF8}{bsmi}

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{HW}{Lee}{MS student of Natinal Tsing Hua Univ. majored in EE Dept.} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
	\section{contact}
		Taipei, Taiwan R.O.C.
		0922-118-303		
		\href{mailto:tony123930@yahoo.com.tw}{tony123930@yahoo.com.tw}
		\href{https://github.com/HW-Lee}{github://HW-Lee}
		\href{https://www.facebook.com/tony123930}{fb://tony123930}
	\section{languages}
		english normal
		chinese mother tongue
	\section{programming} 
		C, C++
		Java, Objective-C
		JavaScript, HTML
		MATLAB, R
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

	\begin{entrylist}
%------------------------------------------------
		\entry
		{2011--2012}
		{Masters {\normalfont of Commerce}}
		{The University of California, Berkeley}
		{\emph{Money Is The Root Of All Evil -- Or Is It?} \\ This thesis explored the idea that money has been the cause of untold anguish and suffering in the world. I found that it has, in fact, not.}
%------------------------------------------------
		\entry
		{2007--2008}
		{Bachelor {\normalfont of Business Studies}}
		{The University of California, Berkeley}
		{Specialization in Commerce}
%------------------------------------------------
	\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

	\begin{entrylist}
%------------------------------------------------
		\entry
		{2012--Now}
		{LEHMAN BROTHERS}
		{Los Angeles, California}
		{\emph{1\textsuperscript{st} Year Analyst} \\
		Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals), managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping. \\
Detailed achievements:
		\begin{itemize}
			\item Learned how to make amazing coffee
			\item Finally determined the reason for \textsc{PC LOAD LETTER}:
			\begin{itemize}
				\item Paper jam
				\item Software issues:
				\begin{itemize}
					\item Word not sending the correct data to printer
					\item Windows trying to print in letter format
				\end{itemize}
				\item Coffee spilled inside printer
			\end{itemize}
			\item Broke the office record for number of kitten pictures in cubicle
		\end{itemize}}
%------------------------------------------------
		\entry
		{2010--2011}
		{LEHMAN BROTHERS}
		{London, United Kingdom}
		{\emph{Summer Intern} \\
		Rated "truly distinctive" for Analytical Skills and Teamwork.}
%------------------------------------------------
		\entry
		{2008-2009}
		{Buy More}
		{Burbank, California}
		{\emph{Computer Repair Specialist} \\
		Worked in the Nerd Herd and helped to solve computer problems by asking customers to turn their computers off and on again.}
%------------------------------------------------
	\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

	\begin{entrylist}
%------------------------------------------------
		\entry
		{2011}
		{Postgraduate Scholarship}
		{School of Business, The University of California}
		{Awarded to the top student in their final year of a Bachelors degree.}
%------------------------------------------------
	\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{communication skills}

	\begin{entrylist}
%------------------------------------------------
		\entry
		{2011}
		{Oral Presentation}
		{California Business Conference}
		{Presented the research I conducted for my Masters of Commerce degree.}
%------------------------------------------------
		\entry
		{2010}
		{Poster}
		{Annual Business Conference, Oregon}
		{As part of the course work for BUS320, I created a poster analyzing several local businesses and presented this at a conference.}
%------------------------------------------------
	\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

	\textbf{professional:} data analysis, company profiling, risk analysis, economics, web design, web app creation, software design, marketing \textbf{personal:} piano, chess, cooking, dancing, running

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}


%----------------------------------------------------------------------------------------

\end{CJK}
\end{document}